Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2017-08-17 paperIEEE.tex
Fix references
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@61 db7c848b-7755-4df2-b763-8796797afa52
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@62 db7c848b-7755-4df2-b763-8796797afa52
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@63 db7c848b-7755-4df2-b763-8796797afa52

@@

Two graphs: Time to render a 4k, 256-step MSAA image of largest ply model and
Livre using 1..16 nodes with all modes (2D, 2D LB, DB, DPlex (over AA steps),
tiles, chunks, pixel, subpixel) (+DFR for Livre)

@@

\bibliographystyle{abbrv}
\bibliography{references/references}

>>>>

\FIXME{add text}

@@

Two graphs: Time to render a 4k, 32-step MSAA image of the 1mm David model and
Livre using 1 to 10 nodes with all modes (2D, 2D LB, DB, DPlex (over AA steps),
tiles, chunks, pixel, subpixel) (+DFR for Livre). The experiments were performed on a cluster using hexacore Intel Xeon E5-2620v3 CPUs (2.4GHz), 16 GB main memory, 4 GBit/s Ethernet and QDR Infiniband. GCC 4.8 has been used with CMake 3.7 release mode settings to compile the software stack.	\FIXME{Not sure about Ethernet.}

@@

\bibliographystyle{abbrv}
\bibliography{references}
